A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-22 tex/codatadp.tex
more

%%% TYPESETTING: Evil hack!!
%We first state the following properties of $\Val^\AST$,
In the following lemma about $\Val^\AST$,
$\muvar( t ) = \smash{\begin{cases}
  x & \text{if $t$ is of the form $\MU {x}.\; u$} \\[-\jot]
  t & \text{otherwise.}
\end{cases}}$

>>>>

%%% TYPESETTING: Evil hack!!
%We first state the following properties of $\Val^\AST$,
In the following lemma about $\Val^\AST$,
$\vphantom{\Bigl(_j}\muvar( t ) = \smash{\begin{cases}
  x & \text{if $t$ is of the form $\MU {x}.\; u$} \\[-\jot]
  t & \text{otherwise.}
\end{cases}}$
